---
title: "World Bank Indicators and United Nations World Happiness Report"
author: "Bruno Barreto, Grace Chun, Jennifer Qin, Tony Choi"
date: "03/01/2020"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
```

## The Data



## Problem Domain Description



## Data Description
```{r}
sk_corruption_line

corruption_mean <- summarize(southkorea_happiness, Perceptions_of_Corruption_Avg = mean(southkorea_happiness$Perceptions.of.corruption))
corruption_max <- summarize(southkorea_happiness, Perceptions_of_Corruption_Max = max(southkorea_happiness$Perceptions.of.corruption))
corruption_min <- summarize(southkorea_happiness, Perceptions_of_Corruption_Min = min(southkorea_happiness$Perceptions.of.corruption, na.rm = TRUE))
```

The corruption values were collected by Transparency International, and measures the perceived degree of corruption in public sectors.
Lower numbers mean that the public views high degrees of corruption within the government, while higher numbers indicate relative improvement. 
The mean value is `r corruption_mean`; the maximum value is `r corruption_max`; and the minimum value is `r corruption_min`.


## Specific Question Analyses


