---
title: "World Bank Indicators and United Nations World Happiness Report"
author: "Bruno Barreto, Grace Chun, Jennifer Qin, Tony Choi"
date: "03/01/2020"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
library("knitr")
```

## Problem Domain Description


## Data Description


## Specific Question Analyses

### What is the relationship between the amount of South Korea's foreign direct investment (FDI) and quality of government? ###

Foreign direct investment (FDI) refers to the net inflows of investment to acquire a lasting management interest (10% or more of voting stock) in an enterprise operating in an economy besides the investor. This measure includes factors, such as:

* Sum of equity capital 
* Reinvestment of earnings
* Short-term and long-term capital 

The net inflow amount is then divided by the respective country's GDP. The higher the value, the more foreign aid a country receives, and vice versa. 

In addition, I analyzed the quality of South Korea's government by closely looking at its perception of corruption and democratic quality. Perception of corruption refers to how South Korean citizens believe whether or not its government makes fair and just choices in regards to the country's functions. Democratic quality includes factors, such as:

* Voice and accountability
* Political stability and absence of violence
* Government effectiveness
* Regulatory quality
* Rule of law
* Control of corruption

Similar to the corruption scale, lower numbers represent more undemocratic conditions, while higher numbers represent more democratic conditions. Perceptions of corruption and democratic quality contribute to a country's overall happiness because the government can exercise huge influence over a citizen's life and happiness based on its policy decisions.

I compared FDI with South Korea's quality of government because I wanted to see if South Korea's desire for foreign aid affects how it treats their people.

For the data analysis method, I first gathered data about South Korea's FDI in 2006 - 2018 from the World Bank, and calculated the average FDI that they received throughout the 12 years. Then, I merged the perceptions of corruption and democratic quality columns to the first table to make direct comparisons. I filtered only to view South Korea's data. 

```{r FDI in South Korea, echo=FALSE}
combined_df
southkorea_fdi_happiness_lineplot
```

From the table and line plot, the data displays that South Korea's perceptions of corruption and democratic quality have remained consistent, while FDI values have flucuated overtime between 2006 - 2018. Therefore, we cannot draw conclusions about how there are strong correlations between South Korea's amount of FDI received annually versus its quality of government, or that South Korea treats its citizens different if its government receives more/less foreign aid. Before starting this analysis, I thought there were would be some correlation between the three variables because I thought about how countries are more suspectible in giving foreign aid to other countries that treat their citizens with fairness and justice. However, it is imperative to point out that FDI and democratic quality was low in 2015. This may have been due to the impeachment of previous South Korean president, Park Geun-Hye, and her bribery scandal, which caused much distrust of South Korea's government of that specific year.














