---
title: "World Bank Indicators and United Nations World Happiness Report"
author: "Bruno Barreto, Grace Chun, Jennifer Qin, Tony Choi"
date: "03/01/2020"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
library("knitr")
```

## Problem Domain Description


## Data Description

In order to address our questions, we will be using two main data sets.
Firstly, we will use the [World Bank's economic indicator data set](https://data.worldbank.org/indicator?tab=all), which contains data on numerous economic indicators from countries around the world and over many years.
And secondly, we will compare these economic indicators to the [UN's World Happiness Report](https://worldhappiness.report/) for 2018 and 2019, which contains extensive data on the reported happiness and the factors behind them for countries across the world.

`r kable(edu_duration_raw)`

In the above data from the World Bank, the indicator column describes what type of data is present in the table while the value column gives the value of that indicator at the time and in the country given by the date and country columns respectively.

`r kable(happ_data_raw)`

In the above Happiness Report data, all column values are _relative_ values that indicate either the reported happiness for a particular country, in the Happiness.score column, or the amount of that reported happiness that is explained by a particular factor, such as in the Explained.by..GDP.per.capita column.
These values are all relative to the reported happiness value for a hypothetical country, Dystopia, that uses the lowest values in all categories from the previous year's report and as such cannot be used for anything other than relative comparisons.

### Summary Analysis

The data for the change in happiness from the UN has a mean of `r Change_in_Happiness_Summary[[4]]`, a median of `r Change_in_Happiness_Summary[[3]]`, a first quartile of `r Change_in_Happiness_Summary[[2]]`, and a third quartile of `r Change_in_Happiness_Summary[[5]]`.
These values show that the average country in the data set showed very little change school enrollment since the quartiles and mean are very close to 0%.

```{r happ_change_plot, echo = FALSE}
Change_in_Happiness_Hist
```

In the above histogram, it can be seen that the change in happiness data has an extreme outlier in the form of Malawi with a `r change_in_happ$Changes.in.happiness.scores[22]` change in relative happiness. 

```{r health, echo = FALSE}
life_average_plot
```

This histogram displays the distribution of average healthy life expectancies of countries from 2000 - 2018. The minimum average health life expectancy in this plot is `r summary_stats[[1]]`years and the maximum average health life expectancy is `r summary_stats[[6]]` years. The average life expectancy for citizens in the countries listed in two data sets is about `r summary_stats[[4]]` years. The histogram reveals the that distrubition is suffiently uneven with some extreme values and there may be factors to further explore that are contributing to it. 

```{r us_debt_over_time, echo = FALSE}
us_debt_over_time_plot
```

The data set of debt in the US from 2006 to 2016 does not have significant outliers, but rather shows a positive trend throughout the years. Although the difference in the debt percentage from 2006 to 2016 is `r us_debt_summary$range`, the debt percentage grew rapidly each year. The correlation between the years and percentages is `r us_debt_correlation[1, 2]` and the average percentage of debt is `r us_debt_summary$mean`.

```{r, echo=FALSE}
sk_corruption_line
```

For one of my variables, I chose to analyze perceptions of corruption in South Korea. The line plot above displays data from 2006 to 2018 for South Korea. According to the UN's World Happiness Report, countries have less perceived corruption if the values are higher. Vice versa, countries have more perceived corruption if the values are lower. Throughout the graph, perceived corruption remains between 0.75 - 0.87, which means that South Korean citizens perceive less corruption from their government and public sector. Therefore, there are no outliers. The mean value is `r corruption_mean`; the minimum value is `r corruption_min`; and the maximum value is `r corruption_max`.

## Specific Question Analyses

### What is the relationship between the amount of South Korea's foreign direct investment (FDI) and quality of government? ###

Foreign direct investment (FDI) refers to the net inflows of investment to acquire a lasting management interest (10% or more of voting stock) in an enterprise operating in an economy besides the investor. This measure includes factors, such as:

* Sum of equity capital 
* Reinvestment of earnings
* Short-term and long-term capital 

The net inflow amount is then divided by the respective country's GDP. The higher the value, the more foreign aid a country receives, and vice versa. 

In addition, I analyzed the quality of South Korea's government by closely looking at its perception of corruption and democratic quality. Perception of corruption refers to how South Korean citizens believe whether or not its government makes fair and just choices in regards to the country's functions. Democratic quality includes factors, such as:

* Voice and accountability
* Political stability and absence of violence
* Government effectiveness
* Regulatory quality
* Rule of law
* Control of corruption

Similar to the corruption scale, lower numbers represent more undemocratic conditions, while higher numbers represent more democratic conditions. Perceptions of corruption and democratic quality contribute to a country's overall happiness because the government can exercise huge influence over a citizen's life and happiness based on its policy decisions.

I compared FDI with South Korea's quality of government because I wanted to see if South Korea's desire for foreign aid affects how it treats their people.

For the data analysis method, I first gathered data about South Korea's FDI in 2006 - 2018 from the World Bank, and calculated the average FDI that they received throughout the 12 years. Then, I merged the perceptions of corruption and democratic quality columns to the first table to make direct comparisons. I filtered only to view South Korea's data. 

```{r FDI in South Korea, echo=FALSE}
combined_df
southkorea_fdi_happiness_lineplot
```

From the table and line plot, the data displays that South Korea's perceptions of corruption and democratic quality have remained consistent, while FDI values have flucuated overtime between 2006 - 2018. Therefore, we cannot draw conclusions about how there are strong correlations between South Korea's amount of FDI received annually versus its quality of government, or that South Korea treats its citizens different if its government receives more/less foreign aid. Before starting this analysis, I thought there were would be some correlation between the three variables because I thought about how countries are more suspectible in giving foreign aid to other countries that treat their citizens with fairness and justice. However, it is imperative to point out that FDI and democratic quality was low in 2015. This may have been due to the impeachment of previous South Korean president, Park Geun-Hye, and her bribery scandal, which caused much distrust of South Korea's government of that specific year.

### How does the amount of government debt in the US affect the perceptions of corruption?

The government debt in the US is taken from the World Bank and the perceptions of corruption is taken from the UN Happiness data. The debt is defined by the percentage of GDP in the United States, while the perceptions of corruption is a score where the higher the number, the more corruption is perceived in the country.

My data analysis method was to take the data of the perceptions of corruptions, and multiplied by 100 so it is easier to compare with the debt percentage on the plot. Since the happiness data only dates back to 2006, I filtered out the years for greater than or equal to 2006 for both of the data sets. I selected only the relevant columns and had to rename some of them like the years so they match up nicely during the left join process. I then plotted the data using the point and line plots and added in a line of best fit to show a correlation.

```{r corruption_debt, echo = FALSE}
us_debt_corruption_plot

```

The correlation between the changes in debt and the changes in the perceptions of corruption is `r debt_corruption_correlation[1, 2]`.

With such a high correlation value of `r debt_corruption_correlation[1, 2]`, it is quite clear that the relationship between the two is as such: the rise in debt in the US results in the rise of the perception of corruption. Taking a look at 2013 to 2015, we can see that the debt percentage stabilizes with a change of `r debt_corruption[8, "debt"]` to `r debt_corruption[10, "debt"]`, and the perception of corruption decreases during the same years, from `r debt_corruption[8, "Perceptions.of.corruption"]` to `r debt_corruption[10, "Perceptions.of.corruption"]`. This shows that even if the debt percentage stagantes, the perceptions of corruption goes down. Then again in 2015, the debt rises again to `r debt_corruption[11, "debt"]`, and as a result, the perception of corruption rises to `r debt_corruption[11, "Perceptions.of.corruption"]`.

### Does a country's education determine or influence the happiness of its citizens?

In order to answer the question of whether education determines happiness for citizens, data on primary school enrollment and on years of compulsory education were taken from the World Bank data set to act as meaures of education while the relative reported happiness and change in happiness were taken from the UN Happiness report to act as measures of happiness by country.

In order to answer this question the years of compulsory education and reported happiness in 2018 were taken, cleaned to ensure that only countries in both data sets were included, then plotted against each other to show the correlation between education and happiness. In addition to this, the difference in primary school enrollment and in reported happiness from 2017 to 2018 were taken, cleaned of countries not present in both data sets, and plotted against each other to show if happiness changes alongside education.

```{r edu_happ, echo = FALSE}
kable(data_set_to_display)
Current_Education_Happiness_Plot
```

```{r edu_happ_change, echo = FALSE}
kable(change_in_happ_to_display)
Change_in_Education_Happiness_Plot
```

In the above plots, the corellation between Years of education and Happiness was `r current_cor` and the correlation between change in primary school enrollment and education was `r change_cor`.

From the shallow slopes, spread out data points, and low correlation values it can be concluded that education is not a predominant factor in the happiness of a country. The fact that the data points are all spread out and not concentrated along a line or a curve suggest that the effect of education on happiness is less significant than it is for other factors. Thus, it can be ultimately concluded that since the slope of the plot is positive, an increase in education is correlated with an increase in happiness, but since the correlation value is so low, it cannot be concluded that the correlation is a significant one.

### Is there a correlation between health expenditure and healthy life expectancy?

The health expenditure dataset includes a value that is the the percent of Gross Domestic Product(GDP), a representation of the monetary value of goods and services, that each country is spending on health care costs within a year. The question attempts to answer if the % of GDP spent contributes to higher or lower life expectancies. I took the average percent of GDP spent on healthcare and compared it to the average life expectancies for each country. 

```{r health table , echo = FALSE}
kable(expectancy_table)
```

```{r health, echo = FALSE}
Health_plot
```

It appears that there is a slight relationship between average % of GDP spent on health care and life expectancy with a correlation of `r correlation[[2]]`. The average health expenditure of countries is `r summary_spend[[4]]` % of GDP and the average life expectancy of countries is `r summary_life[[4]]` years. Since the correlation is weak, this reveals that spending a high percentage of GDP on health care doesn't necessarily result in higher life expectancy in a country as countries that have spent less % of GDP on healthcare have shown to have high average life expectancy. 
